Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-07-24 paper/main.tex
(small) revision of results

% HOW TO WRITE METHODS SEXTION
% first paragraph (cause most readers don't read methods beforehand
% summarizes the overall approach to the problem outlined in the intro
% key innovative methods that were developed
% -> gist of the methods that were used
The goal of this study was to exploratorily investigate how the PPA responds to
auditory cues embedded in a naturalistic audio-only stimulus. We further aimed
at comparing these results to results to an audio-visual naturalistic stimulus
and to results from a dedicated visual localizer experiment.

We did this by using GLM... blabla...
% subsequent paragraphs start with a sentence or two
% that set up the question that the paragraph answers
% e.g. ``To verify that there are no artifacts..''
% What is the test-retest reliability of our measure?''
% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
% Middle of the paragraph presents data and logic that pertain to the question,
% paragraph ends with a sentence that answers the question
% For example, it may conclude that none of potential artifacts were detected.
% Each paragraph convinces the reader of answer given in its last sentence.
% The result of each paragraph is a logical statement

@@

% why we did different contrasts
We tested a variety of contrasts to ensure\dots ???

@@

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% intro
We combined different event categories to create eight contrasts that provided
different congruency with the spatial layout hypothesis and different amount of
data/events.
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiform gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = retrosplenial cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).

% AV
% intro
We also created five contrasts for the audio-visual stimulus by using different
kind of cuts to be able to compare results across perceptual modalities.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show significant bilateral clusters in lateral occipital cortex

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA
        overlaid on the MNI152 T1-weighted head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.}
    \label{fig:stability-slices}
\end{figure*}

\subsection{primary contrasts}
% intro
\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by the audio-description's narrator
(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% precuneus
Two homologous clusters in the ventral precuneus extending into the
retrosplenial cortex.
% PPA
Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, cluster is at borders of the
areas}.
% LOC
And finally, two homologous clusters in the superior lateral occipital cortex.

% AV
% intro
\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% LOC
Two clusters in the superior lateral occipital cortex (left bigger than right).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex,  occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
        Black: outline of overlapping individual PPA ROIs.
        \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report reason here, too: which
subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% why
Analysis in group space (Z>3.4, p<.05 cluster-corrected) was performed for
better comparison of results across participants.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
and AV $t$-contrast and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).

@@

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).

% AO
AO stimulus shows bilateral clusters in nine subjects, and one significant cluster in the
left hemisphere in sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.

% AV
AV shows homologous clusters in five subjects, and unilateral right clusters in
seven subjects (of which one subjects also yielded just a unilateral cluster in
the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere

@@

\subsection{Bland-Altman-Plots}
% why
To better depict the agreement (and difference) between brain responses to the
visual localizer and contrast 1 of the AO paradigm, we created
Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
% what do Bland-Altman-Plots show?
The plots for the 14 subjects show the mean of z-values of two spatially
corresponding voxels in unthresholded z-maps on the x-axis and their difference
on the y-axis (dedicated localizer minus AO stimulus).
% masking
We constrained the number of voxels to voxels in the occipital and temporal
lobes (gray) using the (probabilistic) Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment} to voxels located in the
PPA overlap of all subjects (blue), and voxels in the individual PPA
ROI(s)(red).

% what we can see
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (KDE plot for the x-axis).
% but
Values above the horizontal line depict voxels that show a higher z-value in the
dedicated localizer, values below the horizontal line depict voxels that show
higher z-values in the AO stimulus.

>>>>

% summary of methods: AO
We used conventional GLM contrast to exploratorily investigate how the PPA
responds to auditory cues embedded in a naturalistic audio-only stimulus.
% summary of methods: AV
We compare these results to results to an audio-visual naturalistic stimulus and
to results from a dedicated visual localizer experiment.

% subsequent paragraphs start with a sentence or two
% that set up the question that the paragraph answers
% e.g. ``To verify that there are no artifacts..''
% What is the test-retest reliability of our measure?''
% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
% Middle of the paragraph presents data and logic that pertain to the question,
% paragraph ends with a sentence that answers the question
% For example, it may conclude that none of potential artifacts were detected.
% Each paragraph convinces the reader of answer given in its last sentence.
% The result of each paragraph is a logical statement

@@

% why we did different contrasts
Despite having chosen a primary contrasts which we assumed to give the best
results, we created a variety of contrasts to test if our approach yielded
similar results across a variety of contrasts.

@@

% AO eight contrasts
For the analysis of the AO stimulus, we combined different event categories to
create eight contrasts that provided different amount of data/events and
decreasing congruency with the spatial layout hypothesis.
% results in PPA
Six of eight AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap.\todo[inline]{which is temporal occipital
fusiform gyrus regarding to co-registered Harvard-Oxford Cortical Structural
Atlas}
% Precuneus = retrosplenial cortex ?
Six of eight contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts. Nevertheless, results are sensible to the amount of
data used in the contrasts and it's congruency with the spatial layout
hypothesis.

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        Contrasts provide decreasing congruency with the spatial layout
        hypthesis and/or progressively less data/events. The overlap across
        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).  Blue: contrasts 1-7 for the
        audio-description (see Table \ref{tab:ao-contrasts}.  Red: contrasts 1-5
        for the audio-visual movie (see Table \ref{tab:av-contrasts}.  Black:
        outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.} \label{fig:stability-slices}
    \end{figure*}

\subsection{primary contrasts}
% intro
For the primary contrast of the AO and AV stimulus, we report results on a group
level, on an individual level. Finally, we compare individual results of the AO
stimulus to the dedicated localizer paradigm.

\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by narrator (\texttt{geo, groom > all
non-geo} yielded six significant clusters (see Table \ref{tab:res-ao-group1},
Figure \ref{fig:group-slices}).
% PPA
First, two fall into the anterior part of the visual localizer group overlap
mask.
% location
They are located (in part) in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, clusterss are at borders of the
areas}.
% precuneus
Second, the contrasts yielded two homologous clusters in the ventral precuneus extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital cortex.

% AV intro
For cross-modal comparison purposes, we also analyzed data from the audio-visual
movie.
% the primary contrast
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex, occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.
% LOC
Two homologous clusters are located in the superior lateral occipital cortex
(left bigger than right).

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
        Black: outline of overlapping individual PPA ROIs      \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report reason here, too: which
subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% why
For better comparison of results across participants, we report results of the
analysis that was performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
and AV $t$-contrast and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).

@@

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).
% subjective threshold
Noteworthy, ROIs were assessed by \citep{sengupta2016extension} by visually
inspecting the unthresholded $z$-maps, and setting a subjectively best fitting
$z$-threshold to isolate the PPA.

% AO
In the current analysis of the AO stimulus, we find significant bilateral
clusters in nine subjects, and one significant cluster in the left hemisphere of sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.

% AV
For the AV stimulus, results show homologous clusters in five subjects, and
unilateral right clusters in seven subjects (of which one subjects also yielded
just a unilateral cluster in the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere

@@

\subsection{Bland-Altman-Plots}
% why
To better depict the agreement (and difference) between indivudal results of the
visual localizer and contrast 1 of the AO paradigm, we created
Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
% what do Bland-Altman-Plots show?
The plots for the 14 subjects show the mean of $z$-values of two spatially
corresponding voxels in unthresholded z-maps on the x-axis and the difference of
$z$-values of these two voxels on the y-axis (dedicated localizer minus AO
stimulus).
% masking
We constrained the number of voxels in three ways. Voxels were spatially
contrained to a) voxels in the occipital and temporal lobes (gray; using the
(probabilistic) Jülich Histological Atlas \citep{eickhoff2005toolbox,
eickhoff2007assignment}), b) voxels located in the PPA overlap of all subjects
(blue), and c) voxels in the individual PPA ROI(s)(red).
% what we can see
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (KDE plot for the x-axis).
% but
Values above the horizontal line depict voxels that show a higher z-value in the
dedicated localizer, values below the horizontal line depict voxels that show
higher z-values in the AO stimulus.

\todo[inlin]{concluding statement for the paragraph}
